Impact of grids and dynamical cores in CESM2.2 on the meteorology and climate of the Arctic

### 2021-05-06 arcticgrids.tex
figure caption

\begin{figure}[t]
\begin{center}
         \includegraphics[width=100mm]{figs/temp_tseries_GRIS.pdf}
\end{center}
\caption{.}
\label{fig:tseries}
\end{figure}

>>>>

\begin{figure}[t]
\begin{center}
         \includegraphics[width=100mm]{figs/temp_tseries_GRIS.pdf}
\end{center}
\caption{Time-series of annual (solid+liquid) precipitation (top) and annual runoff (bottom) integrated over the Greenland Ice Sheet for all six simulations and compared to RACMO3.2. The raw fields are mapped to two target low resolution grids, f19 \& ne30pg2, and using two different remapping methods, conservative ESMF and high order TempestRemap. The remapped values are then integrated over the ice mask of the target grid. This gives four time-series for each simulation (three for f19 \& ne30pg2), with the mean value given by the solid line and shading spanning the extent of the remapped solutions.}
\label{fig:tseries}
\end{figure}
